GMU MS SWE Handbook\\{\large A Handbook For the Masters of Software Engineering program at George Mason University

### 2024-08-10 faculty.tex
updates

\chapter{Research}
This section focuses on paper publication, which is a major component in getting your name out there and of course in your departmental evaluation.

\section{What is needed for tenure?}

Publications are a major component of tenure evaluation. There are no specific numbers of papers or which conferences/journals are required, but typically you need to have a good number of papers in top venues to get tenure.  Also work that won awards (e.g., best paper awards or 10-year most influential awards) also count a lot in tenure evaluation. Citations are not required but work with very high citations would help.

@@

\chapter{Obtaining Funding}
Getting funding is arguably the most important part of getting tenure.  Without funding, you can't pay your students, conference registration and travel, or even your own summer salary. However, writing grant proposals is very different from writing research papers. Thus, most new professors struggle with grant writing at first, but eventually get better at it.

%Like most new professors, I struggled big time grant writing at first, but eventually got better at it.

%, which is very different compared to research papers.   In this chapter, we will discuss the various ways to obtain funding.

\section{For P\&T}
Without a doubt, grants are one of the most, if not \emph{the} most, important factors in P\&T (or any kind of performance) evaluation.  The most common reason for not getting tenure is not having enough funding. In an ideal world, research results, e.g., publications, would be the more important; but in reality, funding is often considered more important for tenure evaluation at most R1 universities.
The amount of funding you have is a direct reflection of your research impact and productivity.  It is also a reflection of your ability to write proposals, manage projects, and work with collaborators. More realistically, grants are needed to pay for your students, travel conference, research equipments, and even your own summer salary.

In general, the more funding you have, the better.  However, the \emph{quality} of the funding is also important.  For example, external NSF grants are more prestigious than an internal grant because they give more money and are also more competitive.  Also, funding from industry, while has a much smaller amount, is often highly competitive, prestigious, and can help show that your research is of interest to industry.  Finally, you should aim to get funding from a variety of sources, including NSF, Defense, industry, and internal grants.  This will show that you are able to work with different types of sponsors and that your research is of interest to a wide range of people.

\section{Types of Funding}
\paragraph{NSF} NSF is the obvious funding source for CS. 
Two things stand out for NSF grants are (i. \emph{transparency}) proposals are evaluated by an independent panel and are based on merit rather than personal connections, and (ii. \emph{autonomy}) the flexibility and freedom given to focus on pure research without the pressure of producing concrete deliverables.

@@

However, these sponsors are good sources of funding and can provide the additional resources (e.g., your "3rd" non-NSF summer month). Note that some defense programs, e.g., Young Investigator Award, are more like NSF grants, with less stringent requirements and no deliverables required.

\subsection{Internal Funding}
These are funds from your university, city, or state (e.g., Virginia has the CCI program that provide ``seed'' grants for researchers from universities in Virginia).  Your ``startup'' package is also be considered as a large funding from an internal source (your university) to kickstart your research. These funding are less competitive than NSF, but they are also less prestigious (e.g., they aren't much and usually don't count as much for tenure).  However, they are good sources of funding to get preliminary results and later apply for traditional grants.

\subsection{Industrial Gifts}
Industrial gifts are \emph{unrestricted funding} from companies such as Amazon, Microsoft, Facebook, and Google. While some are connection-based (e.g., for your ongoing work with a collaborator at Facebook), most are based on the merits of your research.
These are highly competitive and prestigious (e.g., the solicitation is open worldwide, and you compete with top researchers from top places).  
They also show that your research has values and impact beyond academia and is interested to industry. Practically, they are the best kind of funding for three reasons: (1) indirect costs or overheads are typically not levied on these gifts (so you get most of the money), (2) there is no associated timeline by when you should spend them (they give it to you and forget about it), and (3) you can use them for a broader range of things than university and grant/contract funding (e.g., summary salary, equipments, or even bowling events for your group).

>>>>

\chapter{Research}\label{chap:research}
This section focuses on paper publication, which is a major component of P\&T and of course in getting your name out there. P\&T evaluation requires no specific conferences/journals or numbers of papers, but typically you will want to have a good number of papers in top venues. P\&T members or letter writers (obviously) are familiar with top places in your field, and they will definitely look for those in your profile.
Work that won awards, e.g., paper awards, can help a lot in tenure evaluation. Papers with very high citations also help.  Research areas that you started and are now popular also count.  Finally, new research directions that can help get grants are also good.

\section{Venues}

Depending on your research area, you might focus on publishing at top conferences or journals.  You probably should know what's popular in your area already (if not, ask your senior colleagues). If you're at an R1 university, you will want to publish at top venues, and not just any venue.  You should also aim to publish at a variety of venues, and not just one.  This will show that your research is of interest to a wide range of people.

\paragraph{Conferences}
In most CS fields, top conferences are more common and competitive than journals. Each field also has several of such top conferences yearly (e.g., in Software Engineering, ICSE, FSE, ASE, and ISSTA are top four).  They are often scheduled so that if you miss (or get rejected) from one, you can submit to another.

You probably will want to get at least about 2 papers at top places each year. This is an average and so you might have 3 one year and 1 the next. Papers with your students are likely more preferred than papers with your peers (and their students) because it shows that you are mentoring your students well and that the project is lead by your group.

\paragraph{Artifact Evaluation}

\paragraph{Journals}
In some journals are more common and prestigious. Moreover, many areas have top journals in additions to well-known conferences (e.g., Trans. of Software Engr. or TSE is a very well-known journal in Software Engineering, which has 4 major confs.).  Typically, or at least in SE, the common approach is publishing new work to conference and followup work to journals (e.g., so the journal paper is an substantial extension of the conf. paper with new experiments, studies, theorems, etc). In some sense, journals are for more mature work, and conferences are for new ideas.

\paragraph{Short papers, workshops, etc}

\section{Collaboration and co-authorship}
While it's general true that profs. are busy, but for me and probably many others, it's not the main reason.  I do skim every single emails from prospective students, but I ignore most of them because they were quite generic (likely written for dozen of other profs.).  Sometimes they try to "customize" it by mentioning the names of my papers, but

.  So even if I am not busy (e.g., spending time on reddit), I still would not reply to such emails.

\paragraph{Papers with your adviser(s)}

@@

\chapter{Obtaining Funding}\label{chap}
Without a doubt, grants are one of the most, if not \emph{the} most, important factors in P\&T (or any kind of performance) evaluation.  The most common reason for not getting tenure is the lack of funding. Ideally research results, e.g., publications (\autoref{chap:research}), would be the more important thing for a researcher; but in reality, funding is often considered more important for tenure evaluation at most R1 universities.
The amount of funding you have is a direct reflection of your research impact and productivity.  It is also a reflection of your ability to write proposals, manage projects, and work with collaborators. More realistically, grants are needed to pay for your students, travel conference, research equipments, and even your own summer salary.

In general, the more funding you have, the better.  However, the \emph{quality} of the funding is also important.  For example, external NSF grants are more prestigious than an internal grant because they give more money and are also more competitive.  Also, funding from industry, while has a much smaller amount, is often highly competitive, prestigious, and can help show that your research is of interest to industry.  Finally, you should aim to get funding from a variety of sources, including NSF, Defense, industry, and internal grants.  This shows that you can work with different types of sponsors and that your research is of interest to a wide range of people.

\section{Types of Funding}\label{sec:fuding-types}
There are several types of funding sources, including external funding (e.g., NSF, DARPA), internal funding (e.g., from your university), and industrial gifts (e.g., from Amazon or Google).  Each type of funding has its own pros and cons, and you should aim to get funding from a variety of sources.
\subsection{External Funding}\label{sec:external}
\paragraph{NSF} NSF is the obvious funding source for CS. 
Two things stand out for NSF grants are (i. \emph{transparency}) proposals are evaluated by an independent panel and are based on merit rather than personal connections, and (ii. \emph{autonomy}) the flexibility and freedom given to focus on pure research without the pressure of producing concrete deliverables.

@@

However, these sponsors are good sources of funding and can provide the additional resources (e.g., your ``3rd'' non-NSF summer month). Note that some defense programs, e.g., Young Investigator Award, are more like NSF grants, with less stringent requirements and no deliverables required.

\subsection{Internal Funding}\label{sec:internal}
These are funds from your university, city, or state (e.g., Virginia has the CCI program that provide ``seed'' grants for researchers from public universities in Virginia).  Your ``startup'' package is also be considered as a large funding from an internal source (your university) to kickstart your research. These funding are less competitive than NSF, but they are also less prestigious (e.g., they aren't much and usually don't count as much for tenure).  However, they are good sources of funding to get preliminary results and later apply for traditional grants.

\subsection{Industrial Gifts}
Industrial gifts are \emph{unrestricted funding} from companies such as Amazon, Microsoft, Facebook, and Google. While some are connection-based (e.g., for your ongoing work with a collaborator at Facebook), most are based on the merits of your research.
While such unrestricted gifts are not a lot (e.g., \$100K), they are highly competitive and prestigious (e.g., the solicitation is open worldwide, and you compete with top researchers from top places).  
They also show that your research has values and impact beyond academia and is interested to industry. 
They are also very flexible (hence the term unrestricted):  (1) indirect costs or overheads are typically not levied on these gifts (so you get most of the money), (2) there is no associated timeline by when you should spend them (they give it to you and forget about it), and (3) you can use them for a broader range of things than university and grant/contract funding (e.g., summary salary, equipments, or even bowling events for your group).

### 2024-08-10 nnv.tex
updates

\chapter{Summary}\label{sec:summary}

>>>>

\chapter{Basic of Neural Network}\label{sec:basic}

A \emph{neural network} (\textbf{NN})~\cite{Goodfellow-et-al-2016} consists of an input layer, multiple hidden layers, and an output layer. Each layer has a number of neurons, each connected to neurons from previous layers through a predefined set of weights (derived by training the network with data). A \textbf{DNN} is an NN with at least two hidden layers.

%A deep neural network consists of three types of layers: an input layer, multiple hidden layers, and an output layer. Each layer consists of a number of neurons, each connected to neurons from another layers through a predefined set of weights (derived by training the network with data). A network is called a \emph{fully connected feed-forward} neural network (FNN) if it connects every neuron in a layer (i.e., all weights are non-zero) to a neuron in the next layer.

The output of a DNN is obtained by iteratively computing  the  values  of  neurons  in  each  layer.
The value of a neuron in the input layer is the input data. The value of a neuron in the hidden layers is computed by applying an \emph{affine transformation} to values of neurons in the previous layers, then followed by an \emph{activation function} such as the popular Rectified Linear Unit (ReLU) activation.

For this activation, the value of a hidden neuron \(y\) is 
$ReLU(w_1v_1 + \dots{} + w_nv_n + b)$, where \(b\) is the bias parameter of \(y\), \(w_i, \dots, w_n\) are the weights of \(y\), \(v_1,\dots,v_n\) are the neuron values of preceding layer, \(w_1v_1 + \dots + w_nv_n+b\) is the affine transformation, and \(ReLU(x) = \max(x,0)\) is the ReLU activation. The values of a neuron in the output layer is evaluated similarly but it may skip the activation function.
A ReLU activated neuron is said to be \emph{active} if its input value is greater than
zero and \emph{inactive} otherwise.

\paragraph{DNN Verification} Given a DNN \(N\) and a property $\phi$, the \emph{DNN verification problem} asks if $\phi$ is a valid property of $N$.
Typically, $\phi$ is a formula of the form $\phi_{in} \Rightarrow \phi_{out}$, where $\phi_{in}$ is a property over the inputs of $N$ and $\phi_{out}$ is a property over the outputs of $N$.
%This form of properties has been used to encode safety and security requirements of DNNs, e.g., safety specifications to avoid collision in unmanned aircraft~\cite{kochenderfer2012next} and \emph{adversarial robustness}~\cite{katz2017towards} properties desired by all DNNs, in which a small input perturbation does not cause major spikes in the DNN's outputs.
A DNN verifier attempts to find a \emph{counterexample} input to $N$ that satisfies $\phi_{in}$ but violates $\phi_{out}$.  If no such counterexample exists, $\phi$ is a valid property of $N$. Otherwise, $\phi$ is not valid and the counterexample can be used to retrain or debug the DNN~\cite{huang2017safety}.

% Verification tool such as Marabou and nnenum are then applied to the network to prove that the network is safe or identifier counterexample representing small input differences causing large output changes.

% \footnote{This is encoded as the differences of the inputs being within a certain small range  ($\phi_{in}$) implies the differences of the outputs still fall within a certain range in $\phi_{out}$)}.

\begin{wrapfigure}{r}{0.3\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{figure/dnn.pdf}
    \caption{\label{fig:dnn} An FNN with ReLU.}
  \end{wrapfigure}
\paragraph{Example} Fig.~\ref{fig:dnn} shows a simple DNN with two inputs $x_1,x_2$, two hidden neurons $x_3,x_4$, and one output $x_5$. The weights of a neuron are shown on its incoming edges , and the bias is shown above or below each neuron. The outputs of the hidden neurons  are computed the affine transformation and ReLU, e.g., $x_3 = ReLU(-0.5x_1+0.5x_2+1.0)$. The output neuron is computed with just the affine transformation, i.e., $x_5=-x_3+x_4-1$.

A valid property for this DNN is that the output is $x_5 \le 0$ for any inputs $x_1 \in [-1,1], x_2\in[-2,2]$. An invalid property for this network is that $x_5 > 0$ for those similar inputs.
A counterexample showing this property violation is $\{x_1=-1, x_2=2\}$, from which the network evaluates to $x_5=-3.5$. Such properties can capture \emph{safety requirements} (e.g., a rule in an  collision avoidance system in~\cite{kochenderfer2012next,katz2017reluplex} is ``if the intruder is distant and significantly slower than us, then we stay below a certain threshold'') or \emph{local robustness}~\cite{katz2017towards} conditions (a form of adversarial robustness stating that small perturbations of a given input all yield the same output).

%Fig.~\ref{fig:dnn}b shows the same network but with each hidden neuron $x$ split into two neurons $x'$ and $x''$ representing the result of affine transformation on $x$ and ReLU activation on $x'$, respectively, e.g.,  $x_3'=-x_1-0.5x_2-1.0$ and  $x_3'' = ReLU(x_3')$. This ReLU-slitting representation is adopted by \tool{} and other DNN analyses (e.g., ~\cite{katz2017reluplex,wang2018efficient,henriksen2020efficient}) 
% including Reluplex~\cite{katz2017reluplex}, Neurify~\cite{wang2018efficient}, and VeriNet~\cite{henriksen2020efficient},
%because it does not change the semantics or complexity of the problem and is easier to reason about as we will show in \S\ref{sec:overview}.

\section{Affine Transformation}

\section{Activation Function}

\section{Properties of Neural Networks}

\subsection{Robustness}

\subsection{Safety}

\chapter{Verification of Neural Networks}\label{sec:verification}

\section{Complexity}

\chapter{Search Algorithms}

\chapter{Constraint Solving}
\section{SMT}
\section{MILP}
\chapter{Abstraction}

\section{Interval}
\section{Zotope}
\section{Polytope}

\chapter{Popular Techniques and Tools}
\chapter{Verifying the Verifiers}
\chapter{Conclusion}
